---
title: "Introduction to the fars package"
author: "Vadim Bondarenko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the fars package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Intro to Fatality Analysis Reporting System (FARS)

The functions provided in the `fars` package facilitate working with data from the US National Highway Traffic Safety Administration's [Fatality Analysis Reporting System](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars), which is a nationwide census providing the American public yearly data regarding fatal injuries suffered in motor vehicle traffic crashes.


## Installation
You can install the package from GitHub using the `devtools` package:
```{r, eval=FALSE}
devtools::install_github("vadimus202/fars")
```


## Usage Examples

### Copy FARS files into working directory

The package includes sample csv files for 2013-2015 data.
```{r}
library(fars)
library(magrittr)
library(knitr)

my_file <- system.file("extdata", "fars_data.zip", package = "fars")
unzip(my_file, junkpaths = TRUE)
```

### Preview 2015 FARS data
```{r, results='asis'}
file_name <- make_filename(2015)
df <- fars_read(file_name)
df %>% head() %>% kable()
```

### Summarize 2013-2015 data
```{r, results='asis'}
fars_summarize_years(2013:2015) %>% kable()
```

### Plot 2014 accidents on California state map
```{r CA_map, fig.width=8}
fars_map_state(6,2014)
```


